Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-01-27 Thesis/chapter/061-results-emma.tex
finish emma discusssion

\td{plot g and p vs TCal, calc avg of p and g for each gen, append pre-emma to appendix}
%%% PROBLEMS 
Even though the main \textit{optimisands} were minimized as required, the \gls{rf}s were not satisfactory. 
The two main problems were too many independent variables and too many dependent variables. 
Both seem closely related and overcomplicate the optimization, but both come with their own implications. 
Too many independent variables make it harder to distinguish variance due to random error (due to unmeasured and uncontrolled variables) from variance due to dependency of chosen dependent varibales. 
This is mainly because of the curse of dimensionality\cite{friedman1988fitting} which makes it hard to collect enough data for each dimension. 
%
In the here presented optimisation model the data points per independent variable 
(events per predictor variable EPV) are as low as 5. 
By eliminating three independent variables the EVP could rise to 10, which is stated 
as rule of tumb for mulitvariate regression\cite{vittinghoff2007relaxing}. 
The results obtained with limited sample number deliver some insightfulness %are quite respectable. 
considering an EPV of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
and an EVP of around 20 in the original \gls{emma} paper\cite{villanova2010function}. 
%In the original \gls{emma} paper\cite{villanova2010function} the EVP is 20.
%\td{In the original \gls{mars} paper\cite{friedman1991multivariate} the model is said 
%to work well on 20-50 events per predictor varibale.
%In the current model EPV are around 5, which is even low for a conservative 
%rule of thumbs of 10-15 EPV\cite{vittinghoff2007relaxing}.
%Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
%Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
%"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
%}
%
The main problem about too many independent variables specific to this optimisation procedure 
is that the same set of \gls{bf}s will be used to predict all \textit{optimisands}.
This leads to competition between the \gls{bf}s as not all dependent variables may depend on the same independent variables. 
This effect is reinforced by the choice of two independent variables as dependent variables. % (IVDV). 
Independent variables as dependent variables will likely be chosen in \gls{bf}s, 
for including them in the \gls{rf}s is an easy way to reduce the \gls{mse}.
These \gls{bf}s then "take away places" of \gls{bf}s predicting other dependent variables in the \gls{rf}. %\td{(cf. musical chairs)} 
This in turn can lead to wrong predictions and therefore inefficient choice of future samples.

\td{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimisands}
The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ 
were included as dependent variables with the objective to maximize with a relative weight of 0.05 each.
The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
}
%
%Three major flaws behind this consideration became obvious with time: 
%
\
\ds{
(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
The algorithm will tend to include those values into the prediction function for 
all dependent variables and possibly exclude others which have more influence 
on $\gamma$ and $\rho$ (see equations (\ref{eq:emma-G4})? and (\ref{eq:emma-phd4})?).
%
(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
%
(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
\begin{itemize}
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS).
Even if it didn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}
}
\td{look at emma papers}
\td{change G to gamma and write enr to every figure}
\td{in \cite{friedman1991multivariate} the model is said to work well on $\frac{N}{n}$ ratios (aka events per predictor varibale (EPV)) of 20-50. 
EPV is around 5 for this model.
Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
}

>>>>

%%% PROBLEMS 
Even though the main \textit{optimisands} were minimized as required, the \gls{rf}s were not satisfactory. 
The two main problems were too many independent variables and too many dependent variables. 
Both seem closely related and overcomplicate the optimization, but both come with their own implications. 
Too many independent variables make it harder to distinguish variance due to random error (due to unmeasured and uncontrolled variables) from variance due to dependency. % of chosen dependent varibales. 
The difficulty of identifying meaningful correlation is mainly owed to the curse of dimensionality\cite{friedman1988fitting} which makes it hard to collect enough data for each dimension. 
%
%In the here presented optimisation model 
%the data points per independent variable 
%(events per predictor variable EPV) are as low as 5. 
The \gls{epv} (data points per independent varible) are as low as 5 in the here presented optimisation model. % and data acquisition method
By eliminating three independent variables the \gls{epv} could rise to 10, which is stated 
as rule of thumb for mulitvariate regression\cite{vittinghoff2007relaxing}. 
The results obtained with limited sample number deliver some insightfulness %are quite respectable. 
considering an \gls{epv} of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
and an \gls{epv} of around 20 in the original \gls{emma} paper\cite{villanova2010function}. 
%In the original \gls{emma} paper\cite{villanova2010function} the \gls{epv} is 20.
%\td{In the original \gls{mars} paper\cite{friedman1991multivariate} the model is said 
%to work well on 20-50 events per predictor varibale.
%In the current model EPV are around 5, which is even low for a conservative 
%rule of thumbs of 10-15 EPV\cite{vittinghoff2007relaxing}.
%Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
%Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
%"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
%}
%

On the other side, the main problem about too many dependent variables specific to this optimisation procedure 
is that the same set of \gls{bf}s will be used to predict \textbf{all} \textit{optimisands}.
This leads to competition between the \gls{bf}s, as not all dependent variables may depend on the same independent variables. 
This effect is reinforced by the choice of two independent variables as dependent variables. % (IVDV). 
Independent variables as dependent variables will likely be chosen in \gls{bf}s, 
for including them in the \gls{rf}s is an easy way to reduce the \gls{mse} and improve prediction accuracy.
These \gls{bf}s then "take away places" of \gls{bf}s predicting other dependent variables in the \gls{rf}. %\td{(cf. musical chairs)} 
This in turn can lead to wrong predictions and therefore inefficient choice of future samples.

The two independent variables $v{cal}$ and $\lambda$ were included as \textit{optimisands} for two reasons: 
Maximizing the calcination velocity and minimizing the number of \td{layers/layer application iterations} leads to minimization of process time.
This optimization would be better placed in a follow up study. 
The second reason for including independent variables was to check if the model works. 
This idea has two flaws: there is only one set of \gls{bf}s for all \textit{optimisands} and thus additional dependent variables not only complicate the model but make it more difficult to predict the actual dependent variables. The second flaw is that there are obsiously better methods to assess the quality of a model that to make it more complex. Good alternatives would have been leave-one-out or cross validation.

\td{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimisands}
The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ 
were included as dependent variables with the objective to maximize with a relative weight of 0.05 each.
The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
}
%
%Three major flaws behind this consideration became obvious with time: 
%
\
\ds{
(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
The algorithm will tend to include those values into the prediction function for 
all dependent variables and possibly exclude others which have more influence 
on $\gamma$ and $\rho$ (see equations (\ref{eq:emma-G4})? and (\ref{eq:emma-phd4})?).
%
(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
%
(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
\begin{itemize}
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS).
Even if it didn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}
}
%\td{look at emma papers}
%\td{change G to gamma and write enr to every figure}

%\td{in \cite{friedman1991multivariate} the model is said to work well on $\frac{N}{n}$ ratios (aka events per predictor varibale (EPV)) of 20-50. 
%EPV is around 5 for this model.
%Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
%"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
%}
